---
title: "Authenticating with the Kalshi API"
output: html
vignette: >
  %\VignetteIndexEntry{Authenticating with the Kalshi API}
  %\VignetteEngine{quarto::quarto_render}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

The `kalshi` package uses a secure, "Pure R" approach to authentication. Instead of relying on external Python libraries, it interfaces directly with your system's `openssl` tool to perform RSA-PSS signing.

## Prerequisite: OpenSSL
This package requires the `openssl` command-line tool. Most Linux (Pop!_OS) and macOS systems have this pre-installed. You can verify it by running `check_openssl_installed()` in R.

## Step 1: Session Setup
Before making API calls, you must point the package to your private RSA key. This path is stored in a hidden internal environment for the duration of your session.

```{r}
library(kalshi)

# Provide the path to your .key file
kalshi_auth_setup("~/path/to/your/kalshi-key-2.key")
```

## Step 2: Environment Variables
The package looks for your Kalshi Key ID (a UUID) in your system environment. We recommend adding this to your `.Renviron` file:

```{md}
KALSHI_API="your-uuid-here"
```

## How the Authentication Works
When you call a function like `get_kalshi_series()`, the following happens under the hood:

1. **Validation**: `check_kalshi_auth()` ensures you've run the setup.
2. **Signing**: The `sign_kalshi_system()` helper constructs a message (`timestamp + method + path`) and sends it to `openssl` for RSA-PSS signing.
3. **Request**: `httr2` attaches the signature and your Key ID to the headers automatically.

## Security Considerations
* **Key Safety**: Your private key is never read into R memory as a raw string; it is only accessed by the system OpenSSL tool.
* **Git Safety**: Ensure `*.key` and `.Renviron` are in your `.gitignore` to prevent accidental leaks to Codeberg/GitHub.---


## First-Time Setup: Generating Keys

If you do not already have an RSA key pair, you can generate one directly within the package. This will create a private `.key` file on your computer and display a **Public Key**.

```{r}
# This creates 'kalshi-key-2.key' in your current folder
kalshi_create_keypair("kalshi-key-2.key")
```



### Registering with Kalshi
1. Copy the **Public Key** printed in your console.
2. Log in to the [Kalshi Developer Dashboard](
3. Upload the Key: Navigate to the API Keys section and click Add Public Key. Paste your copied block into the field and save.
4. Save your Key ID: Kalshi will generate a unique Key ID (a UUID). This is your public identifier for API calls.


## The Two Faces of OpenSSL

This package utilizes OpenSSL in two distinct ways to ensure both ease of use and cryptographic compliance with Kalshi's V2 API:

### 1. The `openssl` R Package (Key Generation)
We use the [openssl](https://cran.r-project.org/package=openssl) R package for standard cryptographic tasks. Specifically, the function `kalshi_create_keypair()` uses this package to:
* Generate 2048-bit RSA keys.
* Format keys into PEM strings.
* Perform Base64 encoding of final signatures.

### 2. The `openssl` System Binary (RSA-PSS Signing)
Kalshi requires signatures to use **RSA-PSS padding** where the **salt length equals the digest length**. 

Because the high-level R wrappers for OpenSSL do not currently expose the specific salt-length parameters required by Kalshi, the `kalshi` package makes a direct `system2()` call to the `openssl` binary installed on your operating system (e.g., `/usr/bin/openssl`).

## Generating Your Keys

If you don't have a key pair yet, run:

```r
# This requires the 'openssl' R package
kalshi_create_keypair("kalshi-key-2.key")
```

The function will print a **Public Key**. Copy this entire block (including the `BEGIN` and `END` lines) and upload it to your [Kalshi Developer Dashboard](https://trading-api.kalshi.com/dashboard).

## Troubleshooting the System Call

If you encounter an error stating `OpenSSL system call failed`, verify that the binary is available in your terminal:

```bash
which openssl
openssl version
```

On **Pop!_OS** or **Ubuntu**, you can install/update it with:
```bash
sudo apt update && sudo apt install openssl
```
