---
title: "Authenticating with the Kalshi API"
---

```{r}
#| include: false
#| eval: false
```

The `kalshi` package uses a secure, "Pure R" approach to authentication. Instead of relying on external Python libraries, it interfaces directly with your system's `openssl` tool to perform RSA-PSS signing.

## Prerequisite: OpenSSL

This package requires the `openssl` command-line tool. Most Linux and macOS systems have this pre-installed. You can verify it by running:

```{r}
#| eval: false
library(kalshi)
check_openssl_installed()
```

## First-Time Setup: Generating Keys

If you do not already have an RSA key pair, generate one:

```{r}
#| eval: false
generate_kalshi_keypair("kalshi-key.key")
```
This creates a private `.key` file and displays the **Public Key** in your console.

### Registering with Kalshi

1. Copy the **Public Key** printed in your console.
2. Log in to the [Kalshi Developer Dashboard](https://kalshi.com/account/api-keys).
3. Click "Create API Key" and paste your public key.
4. Save the **Key ID** (a UUID) that Kalshi provides.

## Step 1: Environment Variables

Add your Key ID to your `.Renviron` file:

```{r}
#| eval: false
usethis::edit_r_environ()
```

Add this line:

```
KALSHI_API=your-uuid-here
```

Save and restart R.

## Step 2: Session Setup

Before making API calls, point the package to your private RSA key:

```{r}
#| eval: false
kalshi_auth_setup("kalshi-key.key")
```

## Making API Calls

Once authenticated, you can call any function:

```{r}
#| eval: false
# Get your account balance
bal <- get_balance()
cat("Balance: $", bal$balance / 100, "\n")

# Get market data
markets <- get_markets(status = "open", limit = 10)

# Get series information
series <- get_series_list(max_pages = 1)
```

## How Authentication Works

When you call a function like `get_markets()`:
1. **Validation**: `check_kalshi_auth()` ensures you've run the setup.
2. **Signing**: A message (`timestamp + method + path`) is signed using RSA-PSS via the system `openssl` binary.
3. **Request**: `httr2` attaches the signature and your Key ID to the headers.

## Security Considerations

* **Key Safety**: Your private key is never read into R memory; it is only accessed by the system OpenSSL tool.
* **Git Safety**: Ensure `*.key` and `.Renviron` are in your `.gitignore`.

## Troubleshooting

If you see `OpenSSL system call failed`, verify the binary is available:

```bash
which openssl
openssl version
```

On Ubuntu/Debian:

```bash
sudo apt update && sudo apt install openssl
```

On macOS:

```bash
brew install openssl
```
