---
title: "Finding Markets: Series, Events, and Tickers"
---

```{r}
#| include: false
#| eval: false
```

Kalshi organizes everything into a three-level hierarchy. Understanding it is the
key to going from a topic you care about (say, the daily high temperature in
Miami) down to the exact contract you can price and trade.

## The ticker hierarchy

```
KXHIGHMIA                    series   — a recurring market template
KXHIGHMIA-26JUN17            event    — one occurrence (a single day)
KXHIGHMIA-26JUN17-B93.5      market   — one outcome bucket within that event
```

| Level | What it is | Example | Function |
|-------|------------|---------|----------|
| **Series** | A recurring market format | `KXHIGHMIA` (Miami daily high temp) | `get_series_list()`, `get_series()` |
| **Event** | A single occurrence, usually one day | `KXHIGHMIA-26JUN17` | `get_events()` |
| **Market** | One outcome bucket you can buy/sell | `KXHIGHMIA-26JUN17-B93.5` | `get_event_markets()`, `get_markets()` |

The event ticker is `SERIES-YYMMMDD` and the market ticker is
`EVENT-<bucket>`, where the bucket suffix is either:

- `B93.5` — a **range** bucket, e.g. "93° to 94°"
- `T89`   — a **threshold** bucket, e.g. "88° or below" or "97° or above"

## Step 1 — find the series

Series tickers for daily high temperatures follow `KXHIGH<city>` (e.g.
`KXHIGHMIA` Miami, `KXHIGHLAX` Los Angeles, `KXHIGHTDC` Washington DC); lows use
`KXLOWT<city>`. Browse them with `get_series_list()`:

```{r}
#| eval: false
library(kalshi)
library(dplyr)

kalshi_auth_setup("kalshi-key.key")

weather <- get_series_list(category = "Climate and Weather")

weather |>
  filter(grepl("Miami", title, ignore.case = TRUE)) |>
  select(ticker, title, frequency)
```

## Step 2 — find each event (one per day)

Given a series ticker, list its events. Each event is a day, named
`KXHIGHMIA-26JUN17`:

```{r}
#| eval: false
# all events for the series
events <- get_events(series_ticker = "KXHIGHMIA")

# only days that have already resolved
events <- get_events(series_ticker = "KXHIGHMIA", status = "settled")

events$event_ticker
#> "KXHIGHMIA-26JUN17" "KXHIGHMIA-26JUN16" ...
```

If you already know the date, build the event ticker directly — no API call
needed:

```{r}
#| eval: false
build_event_tickers("KXHIGHMIA", "2026-06-17")
#> 2026-06-17
#> "KXHIGHMIA-26JUN17"

# a whole range, named by date, ready for purrr::map()
build_event_tickers("KXHIGHMIA", "2026-06-14", "2026-06-17")
```

## Step 3 — find the markets (buckets) within a day

`get_event_markets()` returns one row per temperature bucket, including the
human-readable range and, once settled, the winner (`result == "yes"`):

```{r}
#| eval: false
mk <- get_event_markets("KXHIGHMIA-26JUN17")

mk |> select(ticker, subtitle, result, last_price)
#> ticker                    subtitle      result  last_price
#> KXHIGHMIA-26JUN17-T89     88° or below  no      0.01
#> KXHIGHMIA-26JUN17-B93.5   93° to 94°    yes     0.99
#> ...
```

You can also pull every bucket across every day in a single call, which is handy
for backfilling history:

```{r}
#| eval: false
get_markets(series_ticker = "KXHIGHMIA")                     # all buckets, all days
get_markets(series_ticker = "KXHIGHMIA", status = "settled") # settled only
get_markets(event_ticker  = "KXHIGHMIA-26JUN17")             # one day's buckets
```

## Parsing the bucket range

The `subtitle` ("93° to 94°") holds the range. Split it into numeric edges,
remembering the threshold buckets only have one number:

```{r}
#| eval: false
library(stringr)

mk |>
  mutate(
    nums     = str_extract_all(subtitle, "\\d+"),
    low_deg  = as.integer(purrr::map_chr(nums, \(x) x[1])),
    high_deg = as.integer(purrr::map_chr(nums, \(x) x[length(x)]))
  ) |>
  select(-nums)
```

## Putting it together — odds over time

Once you have a market ticker, `get_candlesticks()` gives its price history. The
`close` column is the last-traded price; `yes_bid_close` / `yes_ask_close` are
the bid/ask. Prices are in dollars (0.53 = 53¢ = a 53% implied probability).

Candlestick times are **UTC**. To query a specific local time, build the window
in the city's timezone and let R handle daylight saving:

```{r}
#| eval: false
# 9:00 AM Houston time on 2026-06-17 (Central) -> correct UTC automatically
start <- as.integer(as.POSIXct("2026-06-17 09:00:00", tz = "America/Chicago"))
end   <- as.integer(as.POSIXct("2026-06-17 09:59:00", tz = "America/Chicago"))

get_candlesticks("KXHIGHMIA-26JUN17-B93.5", "KXHIGHMIA",
                 period_interval = 60, start = start, end = end) |>
  select(time, bid = yes_bid_close, ask = yes_ask_close, last = close)
```

## The full loop

A common analysis — for each day, the buckets, the morning odds, and the winner
— is just these pieces composed with `purrr`:

```{r}
#| eval: false
library(purrr)

build_event_tickers("KXHIGHMIA", "2026-06-14", "2026-06-17") |>
  imap(\(event_ticker, date)
    get_event_markets(event_ticker) |> mutate(date = date)) |>
  list_rbind()
```

From there, join in `get_candlesticks()` for morning odds and filter
`result == "yes"` for the winning bucket each day.
