---
title: "Getting Started with kalshi"
---

```{r}
#| include: false
#| eval: false
```

The `kalshi` package provides a complete R interface to the Kalshi prediction market API. This guide covers installation, authentication, and common use cases.

## Installation

```{r}
#| eval: false
# Install from local source
devtools::install()

# Or load for development
devtools::load_all()
```

## Authentication Setup

Kalshi uses RSA key-based authentication. You need to:

1. Generate a key pair
2. Upload the public key to Kalshi
3. Store your API Key ID

### Step 1: Generate Keys

```{r}
#| eval: false
library(kalshi)

# Generate RSA key pair
generate_kalshi_keypair("kalshi-key.key")
```

This creates `kalshi-key.key` (private, keep secret) and prints the public key.

### Step 2: Upload to Kalshi

1. Copy the public key from the console
2. Go to [Kalshi API Keys](https://kalshi.com/account/api-keys)
3. Create a new API key and paste your public key
4. Save the Key ID (a UUID like `5a2e774e-7f95-4bee-8e98-f4b29f5d38aa`)

### Step 3: Store Key ID

```{r}
#| eval: false
usethis::edit_r_environ()
```

Add this line to your `.Renviron`:
```
KALSHI_API=your-key-id-here
```

Restart R for changes to take effect.

### Step 4: Authenticate Each Session

```{r}
#| eval: false
library(kalshi)
kalshi_auth_setup("kalshi-key.key")
```

## Basic Usage

### Check Account Balance

```{r}
#| eval: false
bal <- get_balance()
cat("Balance: $", bal$balance / 100, "\n")
cat("Portfolio value: $", bal$portfolio_value / 100, "\n")
```

### Browse Markets

```{r}
#| eval: false
# Get open markets
markets <- get_markets(status = "open", limit = 10)

# Filter by series
weather_markets <- get_markets(series_ticker = "KXHIGHNY", status = "open")
```
### Get Series Information

```{r}
#| eval: false
# List all series
series <- get_series_list()

# Find weather series
weather <- series[grepl("HIGH", series$ticker), ]

# Get specific series details
nyc <- get_series("KXHIGHNY")
```

## Weather Market Analysis

### Get Event Results

```{r}
#| eval: false
# Using simplified date input
results <- get_event_results(
  series_ticker = "KXHIGHNY",
  date = "2026-02-07"
)

# See which bracket won
results[results$result == "yes", c("title", "volume")]
```

### Track Price Evolution

```{r}
#| eval: false
# Get hourly price history
candles <- get_candlesticks(
 ticker = "KXHIGHNY-26FEB07-B26.5",
  series_ticker = "KXHIGHNY",
  start = "2026-02-06",
  end = "2026-02-08",
  period_interval = 60  # hourly
)

# See the price journey
candles[, c("time", "open", "high", "low", "close", "volume")]

# Summary
cat("Started at:", candles$open[1], "%\n")
cat("Ended at:", candles$close[nrow(candles)], "%\n")
```

### Historical Analysis

```{r}
#| eval: false
# Get all settled markets for a series
history <- get_series_history("KXHIGHNY")

# Get settled markets in a date range
recent <- get_settled_markets(
  series_ticker = "KXHIGHNY",
  from = "2026-01-01",
  to = "2026-02-01"
)

# Get markets from the last week
last_week <- get_settled_markets(from = Sys.Date() - 7)
```

## Trading

### Place Orders

```{r}
#| eval: false
# Buy 10 yes contracts at 45 cents
order <- create_order(
  ticker = "KXHIGHNY-26FEB08-B26.5",
  side = "yes",
  action = "buy",
  count = 10,
  yes_price = 45
)

# Market order (no price needed)
order <- create_order(
  ticker = "KXHIGHNY-26FEB08-B26.5",
  side = "yes",
  action = "buy",
  count = 10,
  type = "market"
)
```

### Manage Orders

```{r}
#| eval: false
# View resting orders
orders <- get_orders(status = "resting")

# Cancel an order
cancel_order(order$order_id)

# Amend price
amend_order(order$order_id, yes_price = 50)

# Cancel all orders
cancel_all_orders()
```

### View Portfolio

```{r}
#| eval: false
# Current positions
positions <- get_positions()

# Trade history
fills <- get_fills()

# Settlement history
settlements <- get_settlements()
```

## Date Input Formats

All date parameters accept multiple formats:

```{r}
#| eval: false
# String dates
get_event_results(series_ticker = "KXHIGHNY", date = "2026-02-07")

# R Date objects
get_settled_markets(from = as.Date("2026-01-01"))

# Relative dates
get_settled_markets(from = Sys.Date() - 7)  # Last week

# Date ranges
get_candlesticks(
  ticker = "...",
  series_ticker = "...",
  start = "2026-02-01",
  end = "2026-02-07"
)
```

## Available Weather Series

| Series | Description |
|--------|-------------|
| `KXHIGHNY` | NYC high temperature |
| `KXHIGHLA` | LA high temperature |
| `KXHIGHMIA` | Miami high temperature |
| `KXHIGHCHI` | Chicago high temperature |

Find all series:
```{r}
#| eval: false
series <- get_series_list()
```

## Error Handling

The package uses `cli` for informative error messages:

```{r}
#| eval: false
# If not authenticated
get_balance()
#> Error: Kalshi authentication has not been initialized.
#> ℹ You must provide the path to your private RSA key.
#> ✖ Please run: `kalshi_auth_setup()`.

# If key file missing
kalshi_auth_setup("nonexistent.key")
#> Error: The private key file was not found at: nonexistent.key
```

## Function Reference

See the [Reference](../reference.html) page for complete documentation of all 37 exported functions.
